Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

>>>>

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. We use the GitHub version stated in the parenthesis, and because their performance are in general better than the corresponding release version. 
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.
